---
title: "testing_strategy"
author: "Quoc Dinh Nguyen"
date: "July 16, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=9, fig.height=5) 
library(tidyverse)
library(furrr)
library(tictoc)
theme_set(theme_minimal())
```

## Parameters // these specific values not used in simulation - for indicative purposes
nsim            <- 1000       # Number of simulations
n               <- 280        # Population size (common denominator of all test strategy lengths)
latency         <- 3          # Latency of 1 translates into contagiousness for the day following infection (minimum latency of 1 for this code)
dayinfectious   <- 7
r0              <- 3
probimport      <- 0.000036   # Probability of importing one case per person // Play with this to simulation random importation
diagtimepos     <- 14         # Days where test will remain positive after latency
dayoftest       <- c(0,7)     # Days of testing (week goes from 0 to 6)
stopatdiag      <- 1          # Number of diagnosis at which to stop
randomteststart <- 1          # Randomize day of introduction in relation to testing start day
infectstart1    <- 1          # Start with one person infected day 1

## Testing strategy simulation function
```{r}
testStratSim <- function(nsim = 1000, n = 280, latency = 3, dayinfectious = 7, r0 = 3, probimport = 0.000036, 
                         dayoftest, diagtimepos = 14, stopatdiag = 1, sensitivity = 1, randomteststart = 1, infectstartt1 = 1, qweek = 0, bootstrap = 0, seed = 2019){
   set.seed(seed)
   res <- res_temp <- NULL

      for (i in 1:nsim){
       dayoftest <- (unlist(dayoftest) + floor(runif(1)*14)*randomteststart) %% 14             # Randomize start day of the week if randomteststart==1
       if (qweek==2) {bweek <- 1} else {bweek <- 0}
       df <- matrix(nrow = n,
                    data = c(1:n,
                             rep(0, n),
                             rep(0, n),
                             if (infectstartt1 == 0) {0} else {sample(c(-1, rep(0, n-1)))},    # Use -1 as placeholder for infected
                             rep(0, n),
                             rep(dayoftest, n / length(dayoftest)),
                             rep(0, n),
                             rep(NA, n),
                             rep(NA, n))
                    )
       colnames(df) <- c("id", "t", "infected", "dayinfected", "infectious", "testday", "diagnosed", "infectioustotal", "infectedtotal")
       df[,"infectioustotal"] <- sum(df[,"infectious"])

       # Update daily matrix
       for (j in 1:100000){
             if (sum(df[,"diagnosed"]) >= stopatdiag){
                res_temp <- c(df[1,"t"],                            # Day of end
                              max(df[,"dayinfected"] - latency),    # Diagnostic delay    
                              df[1,"infectedtotal"],                # Cases at end
                              df[1,"t"] * n / 7 * ifelse(qweek==0, 0.5, qweek))    # If qweek==0, then average of n/7*0.5 tests/day, elsen n/7*1 and n/7*2
             } else {
                df[,"t"]                                   <- df[,"t"] + 1
                df[df[,"dayinfected"] > 0,"dayinfected"]   <- df[df[,"dayinfected"] >  0,"dayinfected"] + 1
                df[df[,"dayinfected"] == -1,"dayinfected"] <- 1
                df[df[,"dayinfected"] == 0,"dayinfected"]  <- (rbinom(length(df[df[,"dayinfected"] == 0,"dayinfected"]), 1, 
                                                                       probimport) +
                                                               rbinom(length(df[df[,"dayinfected"] == 0,"dayinfected"]), 1, 
                                                                       ifelse(df[,"infectioustotal"]*r0/dayinfectious/n > 1, 1,
                                                                           df[,"infectioustotal"]*r0/dayinfectious/n))) > 0
                df[,"infected"]                            <- df[,"dayinfected"] > 0
                df[,"infectious"]                          <- 0
                df[df[,"dayinfected"] %in% latency:(latency + dayinfectious - 1) &
                   df[,"diagnosed"] == 0,
                   "infectious"]                           <- 1
                if (bootstrap == 1) {                                    # This section for bootstrap sampling: changes dayoftest to sampling with replacement
                   if (df[1,"t"] %% 14 %in% dayoftest) {
                      df[,"testday"] <- sample(c(rep(df[1,"t"] %% 14, n/length(dayoftest)), rep(-1, n - n/length(dayoftest))))
                   } else {
                      df[,"testday"] <- -1}
                }
                df[df[,"diagnosed"] == 1 |
                   ( df[,"t"] %% 14 == df[,"testday"] |
                     ((df[,"t"] + 7) %% 14 == df[,"testday"])*qweek |   # qweek if full week testing
                     ((df[,"t"] + 3)  %% 14 == df[,"testday"])*bweek |   # bweek if full biweekly testing // add +3, +7, +10 days
                     ((df[,"t"] + 7)  %% 14 == df[,"testday"])*bweek |
                     ((df[,"t"] + 10) %% 14 == df[,"testday"])*bweek
                   ) & df[,"dayinfected"] %in% latency:(latency + diagtimepos - 1) &
                       runif(1) <= sensitivity,    
                                          "diagnosed"]     <- 1
                df[,"infectioustotal"]                     <- sum(df[,"infectious"])
                df[,"infectedtotal"]                       <- sum(df[,"infected"])
             }
       }
       res <- rbind(res, res_temp)
   }
   res     <- tibble(end_time       = res[,1],
                     time_to_end    = res[,2],
                     infected_end   = res[,3],
                     tests_done     = res[,4])
   return(res)
}
```

## Scenarios
```{r}
# Base scenarios (14)
scen1 <- tibble(qweek     = 0,
                dayoftest = list(0 
                                ,c(0, 7)
                ))
scen2 <- tibble(qweek     = 1,
                dayoftest = list(c(0, 7)
                                ,c(0, 3, 7, 10)
                                ,c(0, 1, 2, 3, 4, 7, 8, 9, 10, 11)
                                ,0:13
                ))
scen3 <- tibble(qweek     = 2,
                dayoftest = list(c(0,0))    # For qweek==2 (bweek), set only first day of test (program adds +3, +7, +10)
                )
scen <- bind_rows(scen1, scen2, scen3)

scen <- scen %>% mutate(nsim          = 1000,
                        n             = 280,
                        dayinfectious = 7,
                        probimport    = 0.000036,
                        latency       = 3,
                        r0            = 3,
                        diagtimepos   = 14,
                        sensitivity   = 0.9)

# Secondary analyses
scen_high_probimport  <-           scen %>% mutate(probimport = 0.000714)
scen_sens_latency     <-           scen %>% mutate(latency = 5)
scen_sens_r0          <- bind_rows(scen %>% mutate(r0 = 1.5),
                                   scen %>% mutate(r0 = 2),
                                   scen %>% mutate(r0 = 5))
scen_sens_sens        <- bind_rows(scen %>% mutate(sensitivity = 0.75),
                                   scen %>% mutate(sensitivity = 1))

# Full scenarios (7 tests strategies x 8 sets of parameters)
scen <- bind_rows(scen, scen_high_probimport, scen_sens_latency,scen_sens_r0, scen_sens_sens) 
```

## Run simulation 
```{r}
tic()
future::plan(multiprocess)                                                              # Parallel processing using furrr for purrr::pmap
df_temp <- scen %>% mutate(results = future_pmap(scen, testStratSim, .progress = T))    # future_pmap is furrr's parallel version of pmap (~2-3x faster)
toc()
df_ress <- df_temp %>% unnest(results) 
df_ress <- df_ress %>% rowwise %>% mutate(freqtest = length(unlist(dayoftest)))         # Unlist day of test to frequency of test
```

## Results - Table
```{r}
# Clean column names and clean dataset
df_res <- df_ress %>% group_by(qweek, freqtest) %>% 
   mutate(strategy = paste0(freqtest, "-", qweek) %>% fct_recode(
      `1. 100% every 14 days` = "1-0",
      `2. 50% every 7 days`   = "2-0",
      `3. 100% every 7 days`  = "2-1",
      `4. 50% biweekly`       = "4-1",
      `5. 20% weekdays`       = "10-1",
      `6. 14% daily`          = "14-1",
      `7. 100% biweekly`      = "2-2"
   ))

df_res <- df_res %>% group_by(r0, latency, probimport, sensitivity) %>% 
   mutate(parameters = paste(r0, latency, probimport, sensitivity, sep="-")) %>% ungroup
df_res <- df_res %>% mutate(parameters = fct_relevel(parameters, c("3-3-0.000714-0.9", "5-3-3.6e-05-0.9", "3-3-3.6e-05-0.75",
                                                       "3-3-3.6e-05-0.9", "3-3-3.6e-05-1", "3-5-3.6e-05-0.9", "2-3-3.6e-05-0.9")) %>% 
                                         fct_recode(`20x importation rate` = "3-3-0.000714-0.9",
                                                    `R0 = 5`               = "5-3-3.6e-05-0.9",
                                                    `Sensitivity = 0.75`   = "3-3-3.6e-05-0.75",
                                                    `Primary scenario`     = "3-3-3.6e-05-0.9",
                                                    `Sensitivity = 1`      = "3-3-3.6e-05-1",
                                                    `Latency = 5 days`     = "3-5-3.6e-05-0.9",
                                                    `R0 = 2`               = "2-3-3.6e-05-0.9",
                                                    `R0 = 1.5`             = "1.5-3-3.6e-05-0.9"))
df_res <- df_res %>% select(parameters, strategy, end_time, time_to_end, infected_end, tests_done)

# Summary results
df_summ <- df_res %>% group_by(parameters, strategy) %>% 
   summarise(mean_end_time     = mean(end_time),
             mean_time_to_end  = mean(time_to_end) %>% round(1),
             median_time_to_end  = median(time_to_end) %>% round(1),
             max_time_to_end   = max(time_to_end),
             iqr_time_to_end   = quantile(time_to_end,0.75) - quantile(time_to_end, 0.25),
             mean_infected_end = mean(infected_end) %>% round(1),
             median_infected_end = median(infected_end) %>% round(1),
             sd_infected_end   = sd(infected_end) %>% round(1),
             iqr_infected_end  = quantile(infected_end,0.75) - quantile(time_to_end, 0.25),
             mean_tests_done   = mean(tests_done) %>% round(0),
             sd_tests_done     = sd(tests_done) %>% round(0),
             min_tests_done    = min(tests_done),
             max_tests_done    = max(tests_done),
             iqr_tests_done    = quantile(tests_done,0.75) - quantile(time_to_end, 0.25),
             runs              = n(),
             .groups = "drop_last")
df_summ
```

## Results - Figures
```{r}
# Geom_boxplots
## Function for quantiles
f <- function(x) {
  r <- quantile(x, c(0.1, 0.25, 0.5, 0.75, 0.9), na.rm=T)
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}

## Primary analyses
df_text <- df_res %>% group_by(strategy, parameters) %>% 
   summarise(label_mean_time_to_end  = mean(time_to_end) %>% round(2),
             label_mean_infected_end = mean(infected_end) %>% round(2),
             label_mean_tests_done = mean(tests_done) %>% round(0))

f1 <- ggplot(df_res %>% filter(parameters == "Primary scenario"), 
       aes(x=fct_reorder(strategy, desc(strategy)), y=infected_end)) +
  # geom_boxplot(color="grey17", outlier.shape = NA, size=0.7, fill="black", alpha=0.04) +
   stat_summary(fun.data=f, geom="boxplot", color="grey17", alpha=0.04, outlier.shape = NA, size=0.7, fill="black") +
   geom_jitter(color="darkblue", alpha=0.07) +
   stat_summary(fun=mean, geom="point",color="black", shape=21, stroke=1.2, size=3, fill="darkblue", alpha=0.6) +
   annotate("rect", xmin = 0, xmax = 8, ymin = 22.5, ymax = 30, fill="white") +
   geom_text(data = df_text %>% filter(parameters == "Primary scenario"), aes(label = label_mean_tests_done, y=24)) +
   labs(x ="Testing Strategy",
        y = "Cumulative number of cases at first diagnosis") +
   scale_y_continuous(breaks = seq(0, 20, by = 5)) +
   coord_flip(ylim=c(NA, 26.5)) +
   annotate("text", x = 4, y = 25.5, label = "Mean number of tests conducted", angle = 270) +
   annotate("text", x = 0.5, y = 20.5, label = "Mean") +
   annotate("point", x = 0.5, y = 19.25, color="black", shape=21, stroke=1.2, size=3, fill="darkblue", alpha=0.6)

ggsave("Figure1.png", f1, width=9, height=5)

## Secondary analyses
df_text_sens <- df_res %>% group_by(strategy) %>% 
   summarise(label_mean_time_to_end  = mean(time_to_end) %>% round(2),
             label_mean_infected_end = mean(infected_end) %>% round(2),
             label_mean_tests_done = mean(tests_done) %>% round(0))

f2 <- ggplot(df_res, 
       aes(x=fct_reorder(strategy, desc(strategy)), y=infected_end, fill=fct_rev(parameters))) +
   stat_summary(fun.data=f, geom="boxplot", width = 0.8, position="dodge2") +
   #geom_boxplot(outlier.shape = NA, width = 0.8) +
   labs(x    = "Testing Strategy",
        y    = "Cumulative number of cases at first diagnosis",
        fill = "Parameters") +
   stat_summary(fun=mean, geom="point", shape=21, color="white", stroke=1, size=3.5, fill="darkblue", alpha=0.7) +
   annotate("rect", xmin = 0, xmax = 8, ymin = 37.5, ymax = 47.5, fill="white") +
   geom_text(data = df_text_sens, aes(label = label_mean_tests_done, y=40.5, fill="black")) +
   scale_y_continuous(breaks = seq(0, 35, by = 5)) +
   coord_flip(ylim=c(NA,45)) +
   theme(legend.position = "bottom", legend.direction = "horizontal") +
   scale_fill_hue(breaks = levels(df_res$parameters), labels = levels(df_res$parameters)) +
   annotate("text", x = 4, y = 43, label = "Mean number of tests conducted", angle = 270) +
   annotate("text", x = 1.04, y = 35.25, label = "Mean") +
   annotate("point", x = 1, y = 33, color="black", shape=21, stroke=1.2, size=3, fill="darkblue", alpha=0.6)

ggsave("Figure2.png", f2, width=9, height=5)
```
