---
title: "testing_strategy"
author: "Quoc Dinh Nguyen"
date: "June 5, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=10.5, fig.height=6) 
library(tidyverse)
library(furrr)
library(tictoc)
theme_set(theme_minimal())
```

## Parameters // these specific values not used in simulating - for indicative purposes
nsim            <- 100        # Number of simulations
n               <- 280        # Population size (common denominator of all test strategy lengths)
latency         <- 3          # Latency of 1 translates into contagiousness for the day following infection (minimum latency of 1 for this code)
dayinfectious   <- 8
r0              <- 4
probimport      <- 0          # Probability of importing one case per person // Play with this to simulation random importation
diagtimepos     <- 14         # Days where test will remain positive after latency
dayoftest       <- c(0,7)     # Days of testing (week goes from 0 to 6)
stopatdiag      <- 1          # Number of diagnosis at which to stop
randomteststart <- 1
infectstart1    <- 0          # Start with one person infected day 1

## Testing strategy simulation function
```{r}
testStratSim <- function(nsim = 10, n = 280, latency = 3, dayinfectious = 7, r0 = 2, probimport = 0, 
                         dayoftest, diagtimepos = 14, stopatdiag = 1, sensitivity = 1, randomteststart = 1, infectstartt1 = 1, qweek = 0, bootstrap = 0, seed = 2019){
   set.seed(seed)
   res <- res_temp <- NULL

      for (i in 1:nsim){
       dayoftest <- (unlist(dayoftest) + floor(runif(1)*14)*randomteststart) %% 14    # Randomize start day of the week
       if (qweek==2) {bweek <- 1} else {bweek <- 0}
       df <- matrix(nrow = n,
                    data = c(1:n,
                             rep(0, n),
                             rep(0, n),
                             if (infectstartt1 == 0) {0} else {sample(c(-1, rep(0, n-1)))},    # Use -1 as placeholder for infected
                             rep(0, n),
                             rep(dayoftest, n / length(dayoftest)),
                             rep(0, n),
                             rep(NA, n),
                             rep(NA, n))
                    )
       colnames(df) <- c("id", "t", "infected", "dayinfected", "infectious", "testday", "diagnosed", "infectioustotal", "infectedtotal")
       df[,"infectioustotal"] <- sum(df[,"infectious"])

       # Update daily matrix
       for (j in 1:100000){
             if (sum(df[,"diagnosed"]) >= stopatdiag){
                res_temp <- c(df[1,"t"],                            # Day of end
                              max(df[,"dayinfected"] - latency),    # Diagnostic delay    
                              df[1,"infectedtotal"],                # Cases at end
                              df[1,"t"] * n / 7 * ifelse(qweek==0, 0.5, qweek))    # If qweek==0, then average of n/7*0.5 tests/day, elsen n/7*1 and n/7*2
             } else {
                df[,"t"]                                   <- df[,"t"] + 1
                df[df[,"dayinfected"] > 0,"dayinfected"]   <- df[df[,"dayinfected"] >  0,"dayinfected"] + 1
                df[df[,"dayinfected"] == -1,"dayinfected"] <- 1
                df[df[,"dayinfected"] == 0,"dayinfected"]  <- (rbinom(length(df[df[,"dayinfected"] == 0,"dayinfected"]), 1, 
                                                                       probimport) +
                                                               rbinom(length(df[df[,"dayinfected"] == 0,"dayinfected"]), 1, 
                                                                       ifelse(df[,"infectioustotal"]*r0/dayinfectious/n > 1, 1,
                                                                           df[,"infectioustotal"]*r0/dayinfectious/n))) > 0
                df[,"infected"]                            <- df[,"dayinfected"] > 0
                df[,"infectious"]                          <- 0
                df[df[,"dayinfected"] %in% latency:(latency + dayinfectious - 1) &
                   df[,"diagnosed"] == 0,
                   "infectious"]                           <- 1
                if (bootstrap == 1) {                                    # This section for bootstrap sampling: changes dayoftest to sampling with replacement
                   if (df[1,"t"] %% 14 %in% dayoftest) {
                      df[,"testday"] <- sample(c(rep(df[1,"t"] %% 14, n/length(dayoftest)), rep(-1, n - n/length(dayoftest))))
                   } else {
                      df[,"testday"] <- -1}
                }
                df[df[,"diagnosed"] == 1 |
                   ( df[,"t"] %% 14 == df[,"testday"] |
                     ((df[,"t"] + 7) %% 14 == df[,"testday"])*qweek |   # qweek if full week testing
                     ((df[,"t"] + 3)  %% 14 == df[,"testday"])*bweek |   # bweek if full biweekly testing // add +3, +7, +10 days
                     ((df[,"t"] + 7)  %% 14 == df[,"testday"])*bweek |
                     ((df[,"t"] + 10) %% 14 == df[,"testday"])*bweek
                   ) & df[,"dayinfected"] %in% latency:(latency + diagtimepos - 1) &
                       runif(1) <= sensitivity,    
                                          "diagnosed"]     <- 1
                df[,"infectioustotal"]                     <- sum(df[,"infectious"])
                df[,"infectedtotal"]                       <- sum(df[,"infected"])
             }
       }
       res <- rbind(res, res_temp)
   }
   res     <- tibble(end_time       = res[,1],
                     time_to_end    = res[,2],
                     infected_end   = res[,3],
                     tests_done     = res[,4])
   return(res)
}
```

## Scenarios for first article
```{r}
# Base scenarios (14)
scen1 <- tibble(qweek     = 0,
                dayoftest = list(0 
                                ,c(0, 7)
                ))
scen2 <- tibble(qweek     = 1,
                dayoftest = list(c(0, 7)
                                ,c(0, 3, 7, 10)
                                ,c(0, 1, 2, 3, 4, 7, 8, 9, 10, 11)
                                ,0:13
                ))
scen3 <- tibble(qweek     = 2,
                dayoftest = list(c(0,0))    # For qweek==2 (bweek), set only first day of test (program adds +3, +7, +10)
                )
scen <- bind_rows(scen1, scen2, scen3)

scen <- scen %>% mutate(nsim          = 1000,
                        n             = 280,
                        dayinfectious = 7,
                        probimport    = 0.000036,
                        latency       = 3,
                        r0            = 3,
                        diagtimepos   = 14,
                        sensitivity   = 0.9)

# High probimport
scen_high_probimport  <-           scen %>% mutate(probimport = 0.000714)

# Sensitivity analyses (98)
scen_sens_latency     <- bind_rows(#scen %>% mutate(latency = 2),
                                   scen %>% mutate(latency = 5))

scen_sens_r0          <- bind_rows(scen %>% mutate(r0 = 1.5),
                                   scen %>% mutate(r0 = 2),
                                   scen %>% mutate(r0 = 5))

#scen_sens_diagtimepos <-           scen %>% mutate(diagtimepos = 7) 

scen_sens_sens        <- bind_rows(scen %>% mutate(sensitivity = 0.75),
                                   scen %>% mutate(sensitivity = 1))

# Full scenarios (7 tests strategies x 8 sets of parameters)
#scen <- bind_rows(scen, scen_high_probimport, scen_sens_latency) # Run 3 of 8
#scen <- scen_sens_r0                                              # Run 3 of 8
scen <- scen_sens_sens                                           # Run remaining 2 of 8
```

##Run simulation 
```{r}
# Time and progression markers for simulation
completed_scen <- 0
start_time     <- proc.time()

# Run simulation // for 63 scenarios, nsim = 50 ~ 27 min 
tic()
future::plan(multiprocess)                                                              # Parallel processing using furrr for purrr::pmap
df_temp <- scen %>% mutate(results = future_pmap(scen, testStratSim, .progress = T))    # future_pmap is furrr's parallel version of pmap (~2-3x faster)
toc()
df_ress <- df_temp %>% unnest(results) 
df_ress <- df_ress %>% rowwise %>% mutate(freqtest = length(unlist(dayoftest)))           # Unlist day of test to frequency of test

```

## Keep simulation results
```{r}
df_res20200715.2 <- df_ress # 2 of 8 scenarios, nsim=1000
df_res20200715.1 # 3 of 8 scenarios, nsim=1000
df_res20200714 # First 3 of 8 scenarios, nsim=1000
df_res20200709 # 7 scenarios, nsim=250, seed=2019
df_res20200708
```

## Table
```{r}
df_ress <- bind_rows(df_res20200714, df_res20200715.1, df_res20200715.2) 

# Simplify col names
df_res <- df_ress %>% group_by(qweek, freqtest) %>% 
   mutate(strategy = paste0(freqtest, "-", qweek) %>% fct_recode(
      `1. 100% every 14 days` = "1-0",
      `2. 50% every 7 days`   = "2-0",
      `3. 100% every 7 days`  = "2-1",
      `4. 50% biweekly`       = "4-1",
      `5. 20% weekdays`       = "10-1",
      `6. 14% daily`          = "14-1",
      `7. 100% biweekly`      = "2-2"
   ))
df_res <- df_res %>% group_by(r0, latency, probimport, sensitivity) %>% 
   mutate(parameters = paste(r0, latency, probimport, sensitivity, sep="-")) %>% ungroup
df_res <- df_res %>% mutate(parameters = fct_relevel(parameters, c("3-3-0.000714-0.9", "5-3-3.6e-05-0.9", "3-3-3.6e-05-0.75",
                                                       "3-3-3.6e-05-0.9", "3-3-3.6e-05-1", "3-5-3.6e-05-0.9", "2-3-3.6e-05-0.9")) %>% 
                                         fct_recode(`20x importation rate` = "3-3-0.000714-0.9",
                                                    `R0 = 5`               = "5-3-3.6e-05-0.9",
                                                    `Sensitivity = 0.75`   = "3-3-3.6e-05-0.75",
                                                    `Primary scenario`     = "3-3-3.6e-05-0.9",
                                                    `Sensitivity = 1`      = "3-3-3.6e-05-1",
                                                    `Latency = 5 days`     = "3-5-3.6e-05-0.9",
                                                    `R0 = 2`               = "2-3-3.6e-05-0.9",
                                                    `R0 = 1.5`             = "1.5-3-3.6e-05-0.9"))
df_res <- df_res %>% select(parameters, strategy, end_time, time_to_end, infected_end, tests_done)

# Summary results
df_summ <- df_res %>% group_by(parameters, strategy) %>% 
   summarise(#mean_end_time     = mean(end_time),
             #min_end_time      = min(end_time),
             mean_time_to_end  = mean(time_to_end) %>% round(1),
             median_time_to_end  = median(time_to_end) %>% round(1),
             #sd_time_to_end    = sd(time_to_end) %>% round(1),
             #min_time_to_end   = min(time_to_end),
             max_time_to_end   = max(time_to_end),
             iqr_time_to_end   = quantile(time_to_end,0.75) - quantile(time_to_end, 0.25),
             mean_infected_end = mean(infected_end) %>% round(1),
             median_infected_end = median(infected_end) %>% round(1),
             sd_infected_end   = sd(infected_end) %>% round(1),
             #min_infected_end  = min(infected_end),
             iqr_infected_end  = quantile(infected_end,0.75) - quantile(time_to_end, 0.25),
             mean_tests_done   = mean(tests_done) %>% round(0),
             sd_tests_done     = sd(tests_done) %>% round(0),
             min_tests_done    = min(tests_done),
             max_tests_done    = max(tests_done),
             iqr_tests_done    = quantile(tests_done,0.75) - quantile(time_to_end, 0.25),
             runs              = n(),
             .groups = "drop_last")
df_summ
```

## Figures
```{r}
# Geom_boxplots
## Main results
df_text <- df_res %>% group_by(strategy, parameters) %>% 
   summarise(label_mean_time_to_end  = mean(time_to_end) %>% round(2),
             label_mean_infected_end = mean(infected_end) %>% round(2),
             label_mean_tests_done = mean(tests_done) %>% round(0))

f <- function(x) {
  r <- quantile(x, c(0.1, 0.25, 0.5, 0.75, 0.9), na.rm=T)
  names(r) <- c("ymin", "lower", "middle", "upper", "ymax")
  r
}

f1 <- ggplot(df_res %>% filter(parameters == "Primary scenario"), 
       aes(x=fct_reorder(strategy, desc(strategy)), y=infected_end)) +
  # geom_boxplot(color="grey17", outlier.shape = NA, size=0.7, fill="black", alpha=0.04) +
   stat_summary(fun.data=f, geom="boxplot", color="grey17", alpha=0.04, outlier.shape = NA, size=0.7, fill="black") +
   geom_jitter(color="darkblue", alpha=0.07) +
   stat_summary(fun=mean, geom="point",color="black", shape=21, stroke=1.2, size=3, fill="darkblue", alpha=0.6) +
   annotate("rect", xmin = 0, xmax = 8, ymin = 22.5, ymax = 30, fill="white") +
   geom_text(data = df_text %>% filter(parameters == "Primary scenario"), aes(label = label_mean_tests_done, y=24)) +
   labs(x ="Testing Strategy",
        y = "Cumulative number of cases at first diagnosis") +
   scale_y_continuous(breaks = seq(0, 20, by = 5)) +
   coord_flip(ylim=c(NA, 26.5)) +
   annotate("text", x = 4, y = 25.5, label = "Mean number of tests conducted", angle = 270) +
   annotate("text", x = 0.5, y = 20.5, label = "Mean") +
   annotate("point", x = 0.5, y = 19.25, color="black", shape=21, stroke=1.2, size=3, fill="darkblue", alpha=0.6)

ggsave("Figure1.png", f1, width=9, height=5)

## Sensitivity analyses
df_text_sens <- df_res %>% group_by(strategy) %>% 
   summarise(label_mean_time_to_end  = mean(time_to_end) %>% round(2),
             label_mean_infected_end = mean(infected_end) %>% round(2),
             label_mean_tests_done = mean(tests_done) %>% round(0))

f2 <- ggplot(df_res, 
       aes(x=fct_reorder(strategy, desc(strategy)), y=infected_end, fill=fct_rev(parameters))) +
   stat_summary(fun.data=f, geom="boxplot", width = 0.8, position="dodge2") +
   #geom_boxplot(outlier.shape = NA, width = 0.8) +
   labs(x    = "Testing Strategy",
        y    = "Cumulative number of cases at first diagnosis",
        fill = "Parameters") +
   stat_summary(fun=mean, geom="point", shape=21, color="white", stroke=1, size=3.5, fill="darkblue", alpha=0.7) +
   annotate("rect", xmin = 0, xmax = 8, ymin = 37.5, ymax = 47.5, fill="white") +
   geom_text(data = df_text_sens, aes(label = label_mean_tests_done, y=40.5, fill="black")) +
   scale_y_continuous(breaks = seq(0, 35, by = 5)) +
   coord_flip(ylim=c(NA,45)) +
   theme(legend.position = "bottom", legend.direction = "horizontal") +
   scale_fill_hue(breaks = levels(df_res$parameters), labels = levels(df_res$parameters)) +
   annotate("text", x = 4, y = 43, label = "Mean number of tests conducted", angle = 270) +
   annotate("text", x = 1.04, y = 35.25, label = "Mean") +
   annotate("point", x = 1, y = 33, color="black", shape=21, stroke=1.2, size=3, fill="darkblue", alpha=0.6)

ggsave("Figure2.png", f2, width=9, height=5)

# Geom_bars
df_plot <- df_res
df_plot <- df_plot %>% group_by(qweek, freqtest, probimport) %>%    # Used to plot vlines for mean
  mutate(mean_time_to_end  = mean(time_to_end),
         mean_infected_end = mean(infected_end))

df_text <- df_plot %>% group_by(qweek, freqtest, probimport) %>% 
   summarise(label_mean_time_to_end  = mean(time_to_end) %>% round(2),
             label_mean_infected_end = mean(infected_end) %>% round(2))

# Time to end
ggplot(df_plot, aes(x=time_to_end, fill=factor(qweek))) + 
   geom_bar() +
   xlim(0,30) +
   geom_vline(aes(xintercept = mean_time_to_end )) +
   geom_text(data = df_text, aes(label = label_mean_time_to_end, y = 150, x=15)) +
   facet_grid(vars(freqtest), vars(probimport,qweek)) 


# Cases at end
ggplot(df_plot, aes(x=infected_end, fill=factor(qweek))) + 
   geom_bar() +
   xlim(0,20) +
   geom_vline(aes(xintercept = mean_infected_end )) +
   geom_text(data = df_text, aes(label = label_mean_infected_end, y = 200, x=15)) +
   facet_grid(vars(freqtest), vars(probimport,qweek)) 
```

*** STOP THERE CHARLOTTE, BELOW IS ALL TENTATIVE! ***

## Results and plots
### 1. Overall bar plots for time to diagnosis
```{r}

```

### 2. Overall violin plots for time to diagnosis
```{r}
ggplot(df_res, aes(x=factor(freqtest), y=time_to_end, fill=factor(dayinfectious))) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   ylim(0,60) +
   labs(title = "Days to first diagnosis according to test frequency, days infectious, latency, and R0",
        subtitle = "Horizontal facet: R0\nVertical facet: Latency (days)",
        x = "Testing strategy, days per 14 days",
        y = "Days to first diagnosis",
        fill = "Days infectious") +
   facet_grid(vars(r0), vars(latency))
```
### 3. Overall violin plots for cases at first diagnosis
```{r}
ggplot(df_res, aes(x=factor(freqtest), y=infected_end, fill=factor(dayinfectious))) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   ylim(0,50) +
   labs(title = "Cases at first diagnosis according to test frequency, days infectious, latency, and R0",
        subtitle = "Horizontal facet: R0\nVertical facet: Latency (days)",
        x = "Testing strategy, days per 14 days",
        y = "Cases at first diagnosis",
        fill = "Days infectious") +
   facet_grid(vars(r0), vars(latency))
```
### 4. Simplest case: single case at start, no transmission/interdependence (R0=0), low latency (1), long duration of infectiousness
No difference between strategies and no difference by day infectious. There is no interdependence which could favor a more frequent strategy.

As demonstrated by violin plots
```{r}
ggplot(df_res %>% filter(r0==0, latency==1), aes(x=factor(freqtest), y=time_to_end, fill=factor(dayinfectious))) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   labs(title = "Days to first diagnosis according to test frequency, days infectious, latency=1, and R0=0",
        subtitle = "Vertical facet: Days infectious",
        x = "Testing strategy, days per 14 days",
        y = "Days to first diagnosis",
        fill = "Days infectious") +
   facet_grid(cols=vars(dayinfectious))
```
### 5. More frequent sampling yields smaller average
As demonstrated by violin plots below, e.g.: 
* With latency=8 and R0=4, for testing strategy 1/14 vs 2/14
* With latency=3 and R0=4, for testing strategy 2/14 vs 6/14
```{r}
ggplot(df_res %>% filter(latency==3), aes(x=factor(freqtest), y=time_to_end, fill=factor(dayinfectious))) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   ylim(0,30) +
   labs(title = "Days to first diagnosis according to test frequency, days infectious, and R0",
        subtitle = "Horizontal facet: R0\nVertical facet: Latency of 3 days",
        x = "Testing strategy, days per 14 days",
        y = "Days to first diagnosis",
        fill = "Days infectious") +
   facet_grid(vars(r0), vars(dayinfectious)) + theme_minimal()
```
### 6. Spread of the distribution of time to diagnosis has an impact on the number of cases at first diagnosis
```{r}
ggplot(df_res %>% filter(latency==3, dayinfectious==2, r0==4, freqtest==1),
       aes(x=time_to_end, y=infected_end)) +
   geom_point(alpha=0.2) +
   geom_smooth() +
   labs(title = "Days to first diagnosis using 1/14 testing",
     subtitle = "Latency of 3 days\nDay infectious: 2\nR0=4\nLOESS fit",
     x = "Time to first diagnosis, days",
     y = "Cases at first diagnosis")
```
The linear increase in time to first diagnosis has an exponential increase in cases at first diagnosis. Using the above parameters, a shorter spread of time to diagnosis (above and beyond average time) will reduce the number of cases.

### 7. Back to more sanpling yields smaller averages (5)
But why does the decrease in average occur at those specific parameter combinations?
The existence of thresholds is related to time to break up cycles, so:
1. Transmission is needed (there needs to be cycles to be broken up!)
2. A strategy must "break" cycles of transmission to yield benefits

As demonstrated by violin plots below, no benefit when R0=0
```{r}
ggplot(df_res %>% filter(r0==0), aes(x=factor(freqtest), y=time_to_end, fill=factor(dayinfectious))) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
  # ylim(0,20) +
   labs(title = "Days to first diagnosis according to test frequency",
        subtitle = "R0=0",
        x = "Testing strategy, days per 14 days",
        y = "Days to first diagnosis",
        fill = "Days infectious")
```
But starting at R0=1, benefit perceptible for short days of infectiousness, short lag:
* Only for days infectious = 2, lag = 1, we see a difference between 1/14 and 2/14
```{r}
ggplot(df_res %>% filter(r0==1), aes(x=factor(freqtest), y=time_to_end, fill=factor(dayinfectious))) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   ylim(0,20) +
   labs(title = "Days to first diagnosis according to test frequency",
        subtitle = "R0=1\nLatency of 1 day",
        x = "Testing strategy, days per 14 days",
        y = "Days to first diagnosis",
        fill = "Days infectious")
```
At R0=2, for days infectious=2, the benefit comparing 1/14 and 2/14 is much clearer, will the remaining parameters the same.
At R0=4, for days infections=2,the benefit also occurs between 2/14 and 6/14.
At R0=4, there is now also benefit comparing 1/14 and 2/14 for days infections=8
```{r}
ggplot(df_res %>% filter(r0 %in% c(2,4)), aes(x=factor(freqtest), y=time_to_end, fill=factor(dayinfectious))) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   ylim(0,35) +
   labs(title = "Days to first diagnosis according to test frequency",
        subtitle = "Vertical facet: R0\nLatency of 1 day",
        x = "Testing strategy, days per 14 days",
        y = "Days to first diagnosis",
        fill = "Days infectious") +
   facet_grid(cols=vars(r0))
```
Why is it so? Part of the answer is this: 
* If a testing strategy breaks into a cycle of transmission, it will provide benefits. The longer the cycle (serial generation time), the longer one can do without testing without penalty; the shorter the cycle, the more frequent one should test.
* Once a cycle is broken, there is no added benefit to break it further (i.e. to test more frequently) on the *average*. When comparing 10/14 vs 14/14, the maximal difference between those two strategies is 2 days (5 days in a row 2 days off, twice, for 10/14).
** Under our simulation parameters, because we end the simulation at the first diagnosis, the incremental benefit on the exponential growth, comparing 14/14 vs 10/14 never obtains

The importance of the length of each cycle can be strengthened by looking at various latency times, holding other parameters equal (R0=4, days infectious=2).
We can see below that the benefit between 2/14 and 6/14 is greatly reduced when latency is 9 days.
```{r}
ggplot(df_res %>% filter(r0==4), aes(x=factor(freqtest), y=time_to_end)) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   #ylim(0,15) +
   labs(title = "Days to first diagnosis according to test frequency",
        subtitle = "R0=4\nVertical facet: Latency (days)",
        x = "Testing strategy, days per 14 days",
        y = "Days to first diagnosis",
        fill = "Days infectious") +
   facet_grid(cols=vars(latency), rows=vars(dayinfectious))


ggplot(df_res %>% filter(r0==4, dayinfectious==2, latency==1), aes(x=factor(freqtest), y=time_to_end)) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   #ylim(0,15) +
   labs(title = "Days to first diagnosis according to test frequency",
        subtitle = "R0=4\nVertical facet: Latency (days)",
        x = "Testing strategy, days per 14 days",
        y = "Days to first diagnosis",
        fill = "Days infectious")
```
If you don't like violin plots, let these bar two bar charts convince you.
Looking across (similar ), there is no apparent 
```{r}
ggplot(df_res %>% filter(latency==3, dayinfectious==2), 
       aes(x=time_to_end)) +
   geom_bar() +
   facet_grid(vars(r0),vars(freqtest))
```
But we're not really done yet...

_TODO:
1. Infectiousness to 1 day only (clean cycles to break)
2. Import probability, but no transmission
3. Time to 2 diagnoses
4. Do bootstrap sampling

```{r}
# What we could visualize:
## Frequency plots of time_to_end AND infected_end
## Vs Scatterplot of mean and sd of time_to_end AND mean of infected_end 

### Stratification (or y) by r0, testing strategy, random start, lag period
#### That's a total of 80 scenarios cannot all be on the same page


# Assess relation between testing strategy results with other stratification variables

# FUN
ggplot(df_res %>% filter(latency==3, dayinfectious==2), 
       aes(x=time_to_end)) +
   geom_bar() +
   facet_grid(vars(r0),vars(freqtest))

ggplot(df_res %>% filter(latency==1, dayinfectious==8), 
       aes(x=time_to_end)) +
   geom_bar() +
   facet_grid(vars(freqtest), vars(r0))

ggplot(df_res %>% filter(latency==1), 
       aes(x=infected_end, fill=factor(dayinfectious))) +
   geom_bar(position = position_dodge2(preserve="single")) +
   facet_grid(vars(freqtest), vars(r0))

ggplot(df_res %>% filter(latency==3), 
       aes(x=infected_end, fill=factor(dayinfectious))) +
   geom_ggplot(df_res, aes(x=factor(freqtest), y=infected_end, color=factor(dayinfectious))) +
   geom_jitter(alpha=0.2, width = 0.15) +
   facet_grid(vars(r0), vars(latency))bar(position = position_dodge2(preserve="single")) +
   facet_grid(vars(freqtest), vars(r0))

# SCATTER
p <- ggplot(df_res, aes(x=factor(freqtest), y=time_to_end, fill=factor(dayinfectious))) +
   #geom_jitter(alpha=0.05, width = 0.3) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   ylim(0,80) +
   facet_grid(vars(r0), vars(latency))

ggplot(df_res %>% filter(r0==4, latency==1), aes(x=factor(freqtest), y=time_to_end, fill=factor(dayinfectious))) +
   geom_violin(draw_quantiles = 0.5, adjust=0.8) +
   facet_grid(cols=vars(dayinfectious))

pdf("violin_time_to_end.pdf", width = 10.5, height = 7.5, pointsize = 14, paper="USr")
print(p)
dev.off()  

p <- ggplot(df_res, aes(x=factor(freqtest), y=infected_end, fill=factor(dayinfectious))) +
     #geom_jitter(alpha=0.15, width = 0.3) +
     geom_violin(draw_quantiles = 0.5, adjust=0.8) +
     facet_grid(vars(r0), vars(latency))

pdf("violin_infected_end.pdf", width = 10.5, height = 7.5, pointsize = 14, paper="USr")
print(p)
dev.off()  

```

## Analyses
```{r}
# Check-up analyses to run
## Look at day of introduction to make sure that random
## Looking within the lag period not useful if sampling (ignorability) // Rt, rules of expectation (or some calculus/grammar)

```
